---
title: "Multiple Condition Data Generation Functions Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the multi_con argument in mplusParallel_automation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction 

This vignette demonstrates the usage of the multi_con argument in the mplusParallel_automation function. The multi_con argument allows users to specify whether multiple conditions are being used in a single data_gen function. 

```{r setup, results='hide',message=FALSE,warning=FALSE, echo = T}
library(mplusParallel.automation)
```

# Data Generation

For the purpose of this demonstration we will run a simulation where we simulate binary responses for 12 items across two groups. The sample size (s) is varied and a single item in one group receives a varied DIF effect size (es).

Note that the function expects your data_gen function to directly call packages where necessary. In this case, we are using mirt's simdata function and it is called within as mirt::simdata.

```{r datagen}

data_gen<-"

N = c(500,1000)
dif_effect_sizes = c(0.6, 1)

# Initial item parameters
a <- rep(1, 12) # Assuming all items have equal discrimination
b <- seq(-2, 2, length.out = 12) # Assuming items have varying difficulty levels
for(s in N){
for (es in dif_effect_sizes) {
    # Update discrimination of item 1 for Group B
    a_groupB <- a
    a_groupB[1] <- a[1] + es
    
    # Simulate data for both groups
    group_A <- mirt::simdata(a, b, s/2, itemtype = 'dich')

    group_B <- mirt::simdata(a_groupB, b, s/2, itemtype = 'dich')
    group1 <- matrix(rep(1, s/2))
    group2 <- matrix(rep(2, s/2))
    group <- rbind(group1,group2)
    
    
    # Combine the groups' data
    combined_data <- rbind(group_A, group_B)
    
    # Append to all_data
    data <- cbind(group,combined_data)
}}
"

```

# Mplus .inp file creation

The .inp file for this example can be created using the following code.

```{r}
inp_content <- "
TITLE: TEST
DATA: FILE IS exdat.csv;
VARIABLE:
  Names ARE
group
i1 i2 i3 i4 i5 i6 i7 i8 i9 i10 i11 i12;
USEVARIABLES ARE i1-i12;
GROUPING IS group(1=G1, 2=G2)
ANALYSIS:
TYPE = GENERAL;
PROCESSORS=6;
OUTPUT:
STANDARDIZED;
MODINDICES (ALL);
MODEL:
  trait1 BY 
i1 (a1)
i2 (a2)
i3 (a3)
i4 (a4)
i5 (a5)
i6 (a6);
trait2 BY 
i7 (a7)
i8 (a8)
i9 (a9)
i10 (a10)
i11 (a11)
i12 (a12);
i1-i12 (e);
trait1 @ 1 
trait2 @ 1 
MODEL G1:
MODEL G2:
  trait1 BY 
i1 (a1)
i2 (b2)
i3 (b3)
i4 (b4)
i5 (b5)
i6 (b6);
trait2 BY 
i7 (a7)
i8 (b8)
i9 (b9)
i10 (b10)
i11 (b11)
i12 (b12);
"

# Write to an inp file
writeLines(inp_content, "example_model.inp")

```

# Using the multi_con argument

When using the multi_con argument:
multi_con is set to T

The con_index should be set by placing any for loop condition in quotes. For example, our data_gen function contains:
\n
for(s in N)
for (es in dif_effect_sizes)
\n 
We specify con_index = c('s','es') to correctly track the conditions.

In this case we return the summaries from each replication. All single condition results are supported as well. 



```{r}

res <- mplusParallel_automation(k=5, multi_con = T, data_gen = data_gen, con_index = c('es','s'), results = 'summaries') 

```

We can now examine the results and remove the session folders unless they need to be kept.


```{r, comment= NA}
res[,c(1,29,30,33,34)]

removeParFolders()
```
